 

### 2021-01-26 vertical-thermal-review.Rmd
fig 2 caption

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment, from NEON data.** Current placeholder figure is just one of several+ intended sites. See [issue 2](https://github.com/EcoClimLab/vertical-thermal-review/issues/2) and [issue 20](https://github.com/EcoClimLab/vertical-thermal-review/issues/20). ](NEON_height_profiles/figures/profile_all.png)

>>>>

![**Figure `r fig_NEON_vertical`. Vertical gradients in the biophysical environment for 5/6 sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in growing season (a) leaf area density, (b) proportion light incidence, (c) proportion sun leaves, and July mean ± 1 standard deviation for (d) maximum photosyntehtically active ratiation (PAR), (e) maximum wind speed, (f) minimum humidity, (g) maximum $T_{air}$, and (h) maximum biological temperature, $T_{bio}$. All variables are normalized relative to the height of the top of the canopy (**DETAILS**) and the conditions at the point of lowest measurement.   ([Issue 2](https://github.com/EcoClimLab/vertical-thermal-review/issues/2) and [issue 20](https://github.com/EcoClimLab/vertical-thermal-review/issues/20)) ](NEON_height_profiles/figures/profile_all.png)
